\section{Software Developed by Students}

The challenge and experience of building entire software applications for the institution give students the opportunity to grow outside of a traditional classroom setting, while benefitting the institution with custom applications to solve their unique needs. The software projects the SSDT undertake are unique and specific to the institution. The team receives requests for help from departments across the institution, and then review the requests to determine which projects are feasible and which align within the mission of the team. A number of factors determine which systems we will implemented, including the request’s urgency, value to the institution, and the expected effort required to complete the project. The vast majority of the applications the SSDT build are web applications, using familiar web frameworks that are consistent across all of our applications.

In the six years since the creation of the SSDT, the team has undertaken twelve software systems, nine of which are still actively maintained by the team. Systems have been built to support the specific needs of one department, such as a tool for managing the entire Art department's collection of artifacts, while some serve the entire institution, such as the labor status forms system which is described next.

\subsection{The Labor Status Forms Application}
There is not a large market for the creation of software to support the specific needs of work colleges, considering there are only nine in the United States \cite{WCCMembers, Ecclesia}. At our institution of approximately 1,600 students, every student is required to participate in the work-study program as part of their academic requirements for graduation. Every student works 10-20 hours a week, and each department at the college is allocated a specific number of students. The Labor Office, which regulates all student labor, was using an outdated paper-based process and spreadsheets to track all of this information, resulting in lots of errors. This process not only required extra student labor, but also required students to walk across campus gathering signatures from multiple supervisors and academic advisors to complete their forms. A lean project estimated this process took approximately 114 minutes per student to complete a hire.

The SSDT was asked to develop a custom application that would replace the antiquated process. A new web application was designed and developed to be used by every labor supervisor to hire and fire students. It was built with an administration interface, which allowed for all labor to be maintained within one web application, streamlining the process. The new web application, with its first version completed in 2015, provided the Labor Office with a much needed improvement to their previous process. The same lean project estimated a student hire could be completed in as little as 4 minutes, with significantly less errors.

The new system also opened the door for new challenges and opportunities. The web application replaced the existing process, but it introduced new processes that needed consideration. For example, sometimes employment proof is needed for a student. Now that paper forms didn't exist, a new proof of employment document had to be created from our system. For the next four years, these new features were integrated into the existing system as the customer requested them.

After five years of developing this one system, a large backlog of requests had been received and were not getting integrated. This was largely due to the language selected when we began, as well as five years of code that had drastically improved over time, but old code still lingered that occasionally didn't fit our new standards for quality. In 2019, the team decided to move the web application to a new framework that mirrored the other eight live systems also now managed by the SSDT, reducing the amount of relearning necessary when switching between software systems, as well as eliminating the many mistakes made by previous programmers that still lingered.

This application began as an idea to eliminate the error prone paper-based process, and eventually evolved into an application that is now handling all aspects of student labor. The SSDT is driven to build software solutions for departments across the institution, with an emphasis on building maintainable software. This is why the SSDT has structured their software engineering process in a way that gives the team the necessary time needed to build applications from the ground up, while still being able to run regular maintenance on all other systems.
